I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-09 Paper/Paper_noProof.tex
section 3

\subsection{Neural Network and Verification}

@@

The vector $\hat{\boldsymbol{z}}$ is called post-activation values, 
$\boldsymbol{z}$ is called pre-activation values, 
and $\boldsymbol{z}^{i}_j$ is used to call the $j$-th neuron in the $i$-th layer. 
We use $\boldsymbol{x}$ to denote the vector of input and  $f(\boldsymbol{x})$ to denote the output. Finally, neurons are also called \emph{nodes}, and when we refer to a specific neuron, we use $a,b,c,d$ to denote them, and $W_{a,b}$ to denote the weight from neuron $a$ to $b$. Similarly, for input $\boldsymbol{x}$, we denote by $weight_{\boldsymbol{x}}(a)$
the weight of neuron $a$ when the the input is $\boldsymbol{x}$.

@@

Similarly, for simplicity, we focus on local robustness for the verification problem, altough generalization to other problems pose no problem. 
Local robustness asks to determine whether the output of a neural network will be affected under small perturbations to the input. In formula, if we use a distance $d$, and if the $\boldsymbol{x}_0$ is a ordinary input, then the considered domain $\mathcal{D}=\{x: d(\boldsymbol{x},\boldsymbol{x}_0)<\varepsilon\}$ where $\varepsilon$ is the parameter measuring the size of perturbation. And the problem will be \begin{align*}
	\forall \boldsymbol{x}\in\mathcal{D} \   f(\boldsymbol{x}) = f(\boldsymbol{x}_0).
\end{align*} In some cases, the output is a vector but the aim to get the label of dimension with the minimal value. In this case, the problem can be written as:\begin{align*}
\forall \boldsymbol{x} \in\mathcal{D} \  \min f(\boldsymbol{x}) = \min f(\boldsymbol{x}_0)
\end{align*}

@@

In this paper, we only consider $\ReLU$ function as the activation function: $\sigma(a)=\ReLU(a)=\max(0,a)$. We will consider $L^{\infty}$ norm, that is $$d(\boldsymbol{x},\boldsymbol{x}_0)=\max |\boldsymbol{x}(n)-\boldsymbol{x}_0(n)|,$$ the max value of distance of each dimension.

>>>>

%\subsection{Neural Network and Verification}

@@

The vector $\hat{\boldsymbol{z}}$ is called post-activation values, 
$\boldsymbol{z}$ is called pre-activation values, 
and $\boldsymbol{z}^{i}_j$ is used to call the $j$-th neuron in the $i$-th layer. 
For $\boldsymbol{x}=\vz^0$ the vector of input, we denote by $f(\boldsymbol{x})=\vz^\ell$ the output. Finally, neurons are also called \emph{nodes}, and when we refer to a specific neuron, we use $a,b,c,d$ to denote them, and $W_{a,b} \in \mathbb{R}$ to denote the weight from neuron $a$ to $b$. Similarly, for input $\boldsymbol{x}$, we denote by $weight_{\boldsymbol{x}}(a)$ the weight of neuron $a$ when the the input is $\boldsymbol{x}$. A path $\pi$ will be a sequence 
$\pi=(a_i)_{k \leq  i \leq k'}$ of neurons in consecutive layers, and the weight $w(\pi)=W_{a_k,a_{k+1}} \times \cdots \times  W_{a_{k'-1},a_{k'}}$.

@@

Concerning the verification problem, we focus for simplicity on the usual local robustness question. Local robustness asks to determine whether the output of a neural network will be affected under small perturbations to the input. 
Formally, for an input $\vx$ perturbed by $\varepsilon >0$ under distance $d$, then the DNN is locally $\varepsilon$-robust in $\vx$ whenever:
\begin{align*}
	\forall \boldsymbol{x'} \text{ s.t. } d(x,x')\leq \varepsilon, \text{ we have }  
	argmax_i (f(\boldsymbol{x'})[i]) = argmax_i(f(\boldsymbol{x})[i])
\end{align*}

\iffalse
In some cases, the output is a vector but the aim to get the label of dimension with the minimal value. In this case, the problem can be written as:\begin{align*}
\forall \boldsymbol{x} \in\mathcal{D} \  \min f(\boldsymbol{x}) = \min f(\boldsymbol{x}_0)
\end{align*}

@@

In this paper, we only consider $\ReLU$ function as the activation function: $\sigma(a)=\ReLU(a)=\max(0,a)$.

In this paper, we consider $L^{\infty}$ norm the max value of distance of each dimension, that is $d(\boldsymbol{x},\boldsymbol{x}_0)=\max |\boldsymbol{x}(n)-\boldsymbol{x}_0(n)|$. 
\fi

\section{Value Abstraction for DNN verification}

An efficient and prolific line of work concerning DNN verification has been to develop value abstraction of the network. The idea is to compute upper and lower bounds on the values of (some) neurons in the DNN when the inputs are in a given neighbourhood, in order to conclude on the robustness without needing to compute the values exactly for all inputs.

Consider the simpler abstraction, called the box abstraction \cite{deeppoly}: from the bounds in the input, one compute by the linear step the bound on the next layer, apply the ReLU function, and so on.
For instance, on the DNN example of Fig \ref{fig1},
